Hypertension and microbiome

### 2019-10-21 articletwo.Rmd
Minor

@@

```{r lactobacillus prevalence}
dset.genus.salt %>%
    summarize(lacto_detected = sum(lacto.prevalent),
              n = n(),
              ratio = lacto_detected/n) %>%
    kable
```

>>>>

Number of significant associations `r sum(pull(dset.deseq.signf, qval) < 0.05)` for 
`r pull(dset.deseq.signf, Feature)  %>% unique %>% length` features. Largest p.value is 
`r max(pull(dset.deseq.signf, qval))`

@@

```{r lactobacillus prevalence}
prune_lactobacillus(pseq.genus.salt, drop = FALSE) %>%
    summarize(lacto_detected = sum(lacto.prevalent),
              n = n(),
              ratio = lacto_detected/n) %>%
    kable
```
